---
output: 
  github_document:
    toc: false
    fig_width: 10.08
    fig_height: 6
tags: [r, reports]
vignette: >
  \usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

# circus

```{r, echo = FALSE, results='hide', message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  tidy.opts=list(width.cutoff=60),
  tidy=TRUE,
  fig.path = "README-"
)
options(knitr.kable.NA = '',
        digits = 4,
        width=60)

library(rstanarm)
rstan::rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores(),
        digits=2)
```







***The Circus of Monsters!***

`circus` contains a variety fitted models to help the systematic testing of other packages.


## Installation


Run the following:

```{r eval=FALSE, message=FALSE, warning=FALSE}
install.packages("devtools")
devtools::install_github("easystats/circus")
```
```{r message=FALSE, warning=FALSE}
library("circus")
```

## How to use it

You can use the package in your `testthat` block by directly calling the models. However, for it to work on **travis**, it is easier to directly download them from github with the `download_model` in the [`insight`](https://github.com/easystats/insight) package:

```{r eval=FALSE, message=FALSE, warning=FALSE}
test_that("my_function_works", {
  library(insight)

  # model <- circus::lmerMod_1  # Local solution
  model <- insight::download_model("lmerMod_1")
  testthat::expect_equal(myFunction(model), 0.333)
})
```

## Contribute

Feel free to add any model you find missing! Any scary creature for the depth of your mind has its place here!

In order to add models, do the following:

1. Add model creation code in the `README.Rmd`
2. Place the model in the `usethis::use_data()` function (last chunk)
3. Run all the chunks manually: this will create the models, and then the `use_data()` function will save them inside the package's `data` folder
4. Add documentation for your model in the [`R/data.R/`](https://github.com/easystats/circus/blob/master/R/data.R) file
5. Knit the `README.Rmd` file, check and build documentation for the package
6. Upload to github

## List of Models

### Base
```{r, eval=FALSE, warning=FALSE, message=FALSE, results="hide"}
# h-tests
htest_1 <- cor.test(iris$Sepal.Width, iris$Sepal.Length, method = "spearman")
htest_2 <- cor.test(iris$Sepal.Width, iris$Sepal.Length, method = "pearson")
htest_3 <- cor.test(iris$Sepal.Width, iris$Sepal.Length, method = "kendall")
htest_4 <- t.test(iris$Sepal.Width, iris$Sepal.Length)
htest_5 <- t.test(iris$Sepal.Width, iris$Sepal.Length, var.equal = TRUE)
htest_6 <- t.test(iris$Sepal.Width, iris$Sepal.Length)
htest_7 <- t.test(mtcars$mpg ~ mtcars$vs)
htest_8 <- t.test(iris$Sepal.Width, mu = 1)

# ANOVAs
anova_1 <- anova(lm(Sepal.Width ~ Species, data=iris))
aov_1 <- aov(Sepal.Width ~ Species, data=iris)
aovlist_1 <- aov(wt ~ cyl + Error(gear), data=mtcars)

data <- iris
data$Cat1 <- rep(c("X", "X", "Y"), length.out = nrow(data))
data$Cat2 <- rep(c("A", "B"), length.out = nrow(data))

aov_2 <- aov(Sepal.Length ~ Species * Cat1 * Cat2, data=data)
anova_2 <- anova(lm(Sepal.Length ~ Species * Cat1 * Cat2, data=data))
aovlist_2 <- aov(Sepal.Length ~ Species * Cat1+ Error(Cat2), data=data)

aov_3 <- aov(Sepal.Length ~ Species / Cat1 * Cat2, data=data)
anova_3 <- anova(lm(Sepal.Length ~ Species / Cat1 * Cat2, data=data))
aovlist_3 <- aov(Sepal.Length ~ Species / Cat1 + Error(Cat2), data=data)


# GLMs
lm_0 <- lm(mpg ~ 1, data = mtcars)
lm_1 <- lm(mpg ~ wt, data = mtcars)
lm_2 <- lm(mpg ~ wt + cyl, data = mtcars)
lm_3 <- lm(mpg ~ wt * cyl, data = mtcars)
lm_4 <- lm(mpg ~ wt + poly(cyl, 2), data = mtcars)
lm_5 <- lm(mpg ~ wt + poly(cyl, 2, raw=TRUE), data = mtcars)
lm_6 <- lm(mpg ~ wt * as.factor(gear), data = mtcars)
lm_7 <- lm(mpg ~ as.factor(gear) / wt, data = mtcars)

set.seed(123)
mtcars$count <- rpois(nrow(mtcars), 2)

glm_0 <- glm(vs ~ 1, data = mtcars, family="binomial")
glm_1 <- glm(vs ~ wt, data = mtcars, family="binomial")
glm_2 <- glm(vs ~ wt + cyl, data = mtcars, family="binomial")
glm_3 <- glm(vs ~ wt * cyl, data = mtcars, family="binomial")
glm_4 <- glm(vs ~ wt + cyl, data = mtcars, family=binomial(link="probit"))
glm_5 <- glm(formula = count ~ wt + cyl, family = "poisson", data = mtcars)

anova_4 <- anova(lm_0, lm_1, lm_2)
```

### lme4

```{r, eval=FALSE, warning=FALSE, message=FALSE, results="hide"}
library(lme4)

lmerMod_0 <- lme4::lmer(wt ~ 1 + (1|gear), data = mtcars)
lmerMod_1 <- lme4::lmer(wt ~ cyl + (1|gear), data = mtcars)
lmerMod_2 <- lme4::lmer(wt ~ drat + cyl + (1|gear), data = mtcars)
lmerMod_3 <- lme4::lmer(wt ~ drat * cyl + (1|gear), data = mtcars)
lmerMod_4 <- lme4::lmer(wt ~ drat / cyl + (1|gear), data = mtcars)
lmerMod_5 <- lme4::lmer(Petal.Width ~ Cat1 + (1+Cat1|Species), data=data)

merMod_0 <- lme4::glmer(vs ~ 1 + (1|gear), data = mtcars, family="binomial")
merMod_1 <- lme4::glmer(vs ~ cyl + (1|gear), data = mtcars, family="binomial")
merMod_2 <- lme4::glmer(vs ~ drat + cyl + (1|gear), data = mtcars, family="binomial")
merMod_3 <- lme4::glmer(vs ~ drat * cyl + (1|gear), data = mtcars, family="binomial")
merMod_4 <- lme4::glmer(vs ~ cyl + (1|gear), data = mtcars, family=binomial(link="probit"))

anova_lmerMod_0 <- anova(lmerMod_0)
anova_lmerMod_1 <- anova(lmerMod_1)
anova_lmerMod_2 <- anova(lmerMod_2)
anova_lmerMod_3 <- anova(lmerMod_3)
anova_lmerMod_4 <- anova(lmerMod_4)
anova_lmerMod_5 <- anova(lmerMod_5)

anova_lmerMod_6 <- anova(lmerMod_0, lmerMod_1, lmerMod_2)
```



### glmmTMB

```{r, eval=FALSE, warning=FALSE, message=FALSE, results="hide"}
library(glmmTMB)

set.seed(123)
fish <- read.csv("https://stats.idre.ucla.edu/stat/data/fish.csv")
fish$nofish <- as.factor(fish$nofish)
fish$livebait <- as.factor(fish$livebait)
fish$camper <- as.factor(fish$camper)
fish$ID <- sample(1:4, nrow(fish), replace = TRUE)

glmmTMB_1 <- glmmTMB(
  count ~ child + camper + (1 | persons),
  data = fish,
  family = poisson()
)

glmmTMB_zi_1 <- glmmTMB(
  count ~ child + camper + (1 | persons),
  ziformula = ~ child + camper + (1 | persons),
  data = fish,
  family = truncated_poisson()
)

glmmTMB_zi_2 <- glmmTMB(
  count ~ child + camper + (1 | persons),
  ziformula = ~ child + livebait + (1 | persons),
  data = fish,
  family = poisson()
)

glmmTMB_zi_3 <- glmmTMB(
  count ~ child + camper + (1 | persons),
  ziformula = ~ child + livebait + (1 | ID),
  dispformula = ~xb,
  data = fish,
  family = truncated_poisson()
)
```



### GLMMadaptive

```{r, eval=FALSE, warning=FALSE, message=FALSE, results="hide"}
library("GLMMadaptive")
library("lme4")

data(cbpp)

fish <- read.csv("https://stats.idre.ucla.edu/stat/data/fish.csv")
fish$nofish <- as.factor(fish$nofish)
fish$livebait <- as.factor(fish$livebait)
fish$camper <- as.factor(fish$camper)

GLMMadaptive_zi_1 <- GLMMadaptive::mixed_model(
  count ~ child + camper,
  random = ~ 1 | persons,
  zi_fixed = ~ child + livebait,
  data = fish,
  family = GLMMadaptive::zi.poisson()
)

GLMMadaptive_zi_2 <- GLMMadaptive::mixed_model(
  count ~ child + camper,
  random = ~ 1 | persons,
  zi_fixed = ~ child + livebait,
  zi_random = ~ 1 | persons,
  data = fish,
  family = GLMMadaptive::zi.poisson()
)

GLMMadaptive_1 <- GLMMadaptive::mixed_model(
  cbind(incidence, size - incidence) ~ period,
  random = ~ 1 | herd,
  data = cbpp,
  family = binomial
)
```


### Rstanarm

```{r, eval=FALSE, warning=FALSE, message=FALSE, results="hide"}
set.seed(333)

library(rstanarm)

stanreg_lm_0 <- rstanarm::stan_glm(mpg ~ 1, data = mtcars)
stanreg_lm_1 <- rstanarm::stan_glm(mpg ~ wt, data = mtcars)
stanreg_lm_2 <- rstanarm::stan_glm(mpg ~ wt + cyl, data = mtcars)
stanreg_lm_3 <- rstanarm::stan_glm(mpg ~ wt * cyl, data = mtcars)
stanreg_lm_4 <- rstanarm::stan_glm(mpg ~ wt + poly(cyl, 2), data = mtcars)
stanreg_lm_5 <- rstanarm::stan_glm(mpg ~ wt + poly(cyl, 2, raw=TRUE), data = mtcars)
stanreg_lm_6 <- rstanarm::stan_glm(mpg ~ wt * as.factor(gear), data = mtcars)
stanreg_lm_7 <- rstanarm::stan_glm(mpg ~ as.factor(gear) / wt, data = mtcars)

stanreg_glm_0 <- rstanarm::stan_glm(vs ~ 1, data = mtcars, family="binomial")
stanreg_glm_1 <- rstanarm::stan_glm(vs ~ wt, data = mtcars, family="binomial")
stanreg_glm_2 <- rstanarm::stan_glm(vs ~ wt + cyl, data = mtcars, family="binomial")
stanreg_glm_3 <- rstanarm::stan_glm(vs ~ wt * cyl, data = mtcars, family="binomial")
stanreg_glm_4 <- rstanarm::stan_glm(vs ~ wt + cyl, data = mtcars, family=binomial(link="probit"))
stanreg_glm_5 <- rstanarm::stan_glm(vs ~ wt + cyl, data = mtcars, family="poisson")

stanreg_lmerMod_0 <- rstanarm::stan_lmer(wt ~ 1 + (1|gear), data = mtcars)
stanreg_lmerMod_1 <- rstanarm::stan_lmer(wt ~ cyl + (1|gear), data = mtcars)
stanreg_lmerMod_2 <- rstanarm::stan_lmer(wt ~ drat + cyl + (1|gear), data = mtcars)
stanreg_lmerMod_3 <- rstanarm::stan_lmer(wt ~ drat * cyl + (1|gear), data = mtcars)
stanreg_lmerMod_4 <- rstanarm::stan_lmer(wt ~ drat / cyl + (1|gear), data = mtcars)
stanreg_lmerMod_5 <- rstanarm::stan_lmer(Petal.Width ~ Cat1 + (1+Cat1|Species), data=data)

stanreg_merMod_0 <- rstanarm::stan_glmer(vs ~ 1 + (1|gear), data = mtcars, family="binomial")
stanreg_merMod_1 <- rstanarm::stan_glmer(vs ~ cyl + (1|gear), data = mtcars, family="binomial")
stanreg_merMod_2 <- rstanarm::stan_glmer(vs ~ drat + cyl + (1|gear), data = mtcars, family="binomial")
stanreg_merMod_3 <- rstanarm::stan_glmer(vs ~ drat * cyl + (1|gear), data = mtcars, family="binomial")
stanreg_merMod_4 <- rstanarm::stan_glmer(vs ~ cyl + (1|gear), data = mtcars, family=binomial(link="probit"))


stanreg_meanfield_lm_1 <- update(stanreg_lm_1, algorithm="meanfield")
stanreg_fullrank_lm_1 <- update(stanreg_lm_1, algorithm="fullrank")


stanreg_gamm4_1 <- stan_gamm4(Sepal.Width ~ s(Petal.Length), data=iris)
stanreg_gamm4_2 <- stan_gamm4(Sepal.Width ~ Species + s(Petal.Length), data=iris)
stanreg_gamm4_3 <- stan_gamm4(Sepal.Width ~ Species + s(Petal.Length), random = ~ (1 | Cat1), data=data)
```

### BRMS

```{r, eval=FALSE, warning=FALSE, message=FALSE, results="hide"}
library(lme4)
library(brms)
library(dplyr)

data(sleepstudy)
data(mtcars)
zinb <- read.csv("http://stats.idre.ucla.edu/stat/data/fish.csv")

set.seed(123)
sleepstudy$grp <- sample(1:5, size = 180, replace = TRUE)
sleepstudy <- sleepstudy %>%
  group_by(grp) %>%
  mutate(subgrp = sample(1:15, size = n(), replace = TRUE))

brms_mixed_1 <- brm(mpg ~ wt + (1 | cyl) + (1 + wt | gear), data = mtcars)
brms_mixed_2 <- brm(Reaction ~ Days + (1 + Days | Subject), data = sleepstudy)
brms_mixed_3 <- brm(Reaction ~ Days + (1 | grp / subgrp) + (1 | Subject), data = sleepstudy)

brms_mv_1 <- brm(cbind(cyl, gear, carb) ~ wt + hp, data = mtcars)
f1 <- bf(mpg ~ wt + disp + cyl + hp + (1 |CAR| gear))
f2 <- bf(wt ~ disp + cyl + hp + (1 |CAR| gear))
brms_mv_2 <- brm(f1 + f2 + set_rescor(FALSE), data = mtcars)

brms_zi_1 <- brm(bf(count ~ persons + child + camper, zi ~ child + camper), data = zinb, family = zero_inflated_poisson())
brms_zi_2 <- brm(bf(count ~ persons + child + camper + (1 | persons), zi ~ child + camper + (1 | persons)), data = zinb, family = zero_inflated_poisson())
```

## Save
```{r, eval=FALSE, warning=FALSE, message=FALSE, results="hide"}
usethis::use_data(htest_1,
                  htest_2,
                  htest_3,
                  htest_4,
                  htest_5,
                  htest_6,
                  htest_7,
                  htest_8,
                  
                  anova_1,
                  aov_1,
                  aovlist_1,
                  anova_2,
                  aov_2,
                  aovlist_2,
                  anova_3,
                  aov_3,
                  aovlist_3,
                  anova_4,
                  
                  lm_0,
                  lm_1,
                  lm_2,
                  lm_3,
                  lm_4,
                  lm_5,
                  lm_6,
                  lm_7,
                  glm_0,
                  glm_1,
                  glm_2,
                  glm_3,
                  glm_4,
                  glm_5,
                  
                  lmerMod_0,
                  lmerMod_1,
                  lmerMod_2,
                  lmerMod_3,
                  lmerMod_4,
                  lmerMod_5,
                  merMod_0,
                  merMod_1,
                  merMod_2,
                  merMod_3,
                  merMod_4,
                  
                  anova_lmerMod_0,
                  anova_lmerMod_1,
                  anova_lmerMod_2,
                  anova_lmerMod_3,
                  anova_lmerMod_4,
                  anova_lmerMod_5,
                  anova_lmerMod_6,
                  
                  glmmTMB_1,
                  glmmTMB_zi_1,
                  glmmTMB_zi_2,
                  glmmTMB_zi_3,
                  
                  GLMMadaptive_1,
                  GLMMadaptive_zi_1,
                  GLMMadaptive_zi_2,
                  
                  stanreg_lm_0,
                  stanreg_lm_1,
                  stanreg_lm_2,
                  stanreg_lm_3,
                  stanreg_lm_4,
                  stanreg_lm_5,
                  stanreg_lm_6,
                  stanreg_lm_7,
                  stanreg_glm_0,
                  stanreg_glm_1,
                  stanreg_glm_2,
                  stanreg_glm_3,
                  stanreg_glm_4,
                  stanreg_glm_5,
                  stanreg_lmerMod_0,
                  stanreg_lmerMod_1,
                  stanreg_lmerMod_2,
                  stanreg_lmerMod_3,
                  stanreg_lmerMod_4,
                  stanreg_lmerMod_5,
                  stanreg_merMod_0,
                  stanreg_merMod_1,
                  stanreg_merMod_2,
                  stanreg_merMod_3,
                  stanreg_merMod_4,
                  stanreg_meanfield_lm_1,
                  stanreg_fullrank_lm_1,
                  
                  stanreg_gamm4_1,
                  stanreg_gamm4_2,
                  stanreg_gamm4_3,
                  
                  brms_mixed_1,
                  brms_mixed_2,
                  brms_mixed_3,
                  
                  brms_mv_1,
                  brms_mv_2,
                  
                  brms_zi_1,
                  brms_zi_2,
                  
                  
                  overwrite=TRUE)
```