---
output:
  github_document:
    toc: false
    fig_width: 10.08
    fig_height: 6
tags: [r, reports]
vignette: >
  \usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
editor_options:
  chunk_output_type: console
---

# circus

```{r, echo = FALSE, results='hide', message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  tidy.opts = list(width.cutoff = 60),
  tidy = TRUE,
  fig.path = "README-"
)
options(
  knitr.kable.NA = "",
  digits = 4,
  width = 60
)

library(rstanarm)
rstan::rstan_options(auto_write = TRUE)
options(
  mc.cores = parallel::detectCores(),
  digits = 2
)
```







***The Circus of Monsters!***

`circus` contains a variety fitted models to help the systematic testing of other packages.


## Installation


Run the following:

```{r eval=FALSE, message=FALSE, warning=FALSE}
install.packages("remotes")
remotes::install_github("easystats/circus")
library("circus")
```

## How to use it

You can use the package in your `testthat` block by directly calling the models. However, for it to work on **travis**, it is easier to directly download them from github with the `download_model` in the [`insight`](https://github.com/easystats/insight) package:

```{r eval=FALSE, message=FALSE, warning=FALSE}
test_that("my_function_works", {
  testthat::skip_if_not_installed("insight")
  testthat::skip_if_not_installed("curl") # to check internet access
  testthat::skip_if_offline()
  testthat::skip_if_not_installed("httr2") # to download stuff

  # model <- circus::lmerMod_1  # Local solution
  model <- insight::download_model("lmerMod_1")
  testthat::skip_if(is.null(model))
  testthat::expect_equal(myFunction(model), 0.333)
})
```

## Contribute

Feel free to add any model you find missing! Any scary creature for the depth of your mind has its place here!

In order to add models, do the following:

1. Add your model-name in the `usethis::use_data()` function (last chunk) in the `README.Rmd`
2. Add documentation for your model in the [`R/data.R/`](https://github.com/easystats/circus/blob/main/R/data.R) file
3. Now fit your model and save it to the data-folder, using `usethis::use_data(<yourmodel>)`.
4. Check and build documentation for the package (to generate the `.rd`-files)
5. Upload following files to github: `/data/<yourmodel.rda>`, `data.R` and `data.rd`.

**Note** When you build or install the package, it is recommended to do so with following build-options: `R CMD INSTALL --no-multiarch --with-keep.source --no-libs --no-data`. Furthermore, when building the documentation, make sure to **not** build the vignettes.

## Sample data

### Illusion Game

```r{,eval=FALSE}
# Data from Makowski et al., (2023) for the Illusion Game
df <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGameValidation/refs/heads/main/data/study1.csv")
df <- df[c("Participant", "Illusion_Type", "Trial", "RT", "Error", "Illusion_Strength", "Illusion_Difference")]
df$RT <- df$RT / 1000
df <- df[df$Illusion_Strength > 0, ]
df <- df[df$Illusion_Type %in% c("Müller-Lyer", "Delboeuf", "Ebbinghaus", "Vertical-Horizontal", "Ponzo"), ]
write.csv(df, "../data/illusiongame.csv", row.names = FALSE)
```

## How to add models

```{r, eval=FALSE, warning=FALSE, message=FALSE, results="hide"}
lm_1 <- lm(mpg ~ wt, data = mtcars)
usethis::use_data(lm_1, overwrite = TRUE)
```
