---
title: "Bootsrapped data"
output: 
  github_document:
    toc: true
    fig_width: 10.08
    fig_height: 6
  rmarkdown::html_vignette:
    toc: true
    fig_width: 10.08
    fig_height: 6
tags: [r, bootstrapped]
vignette: >
  \usepackage[utf8]{inputenc}
editor_options: 
  chunk_output_type: console
---

# Generate Bootstrapped data

We generated one large sample (the **parent population**, size `1000000`) of two
continuous variables producing a regression coefficient of `0.5`. We then
iteratively extracted a subsample of size `30`, computed 3 types of coefficient
(regular, bootstrapped with 1000 iterations and bootstrapped with 4000
iterations) that were subtracted from the "parent" coefficient. The closer the
value is from 0, and the closer it is from the "true" effect.

## Convenience Functions
```{r eval=TRUE, message=FALSE, warning=FALSE, results='hide'}
generate_parent_population <- function(noise = 1, n = 10000) {
  y <- rnorm(n, 0, 1)
  x <- y + rnorm(n, 0, noise)
  return(data.frame(x = x, y = y, noise = noise))
}

extract_sample <- function(data, n = 30) {
  return(data[sample(nrow(data), n), ])
}

extract_parameters <- function(model, real = 1) {
  data.frame(
    Real = real,
    Coefficient = real - parameters::model_parameters(model)$Coefficient[2],
    Bootstrapped_1000 = real - parameters::model_parameters(model, bootstrap = TRUE, n = 1000)$Coefficient[2],
    Bootstrapped_4000 = real - parameters::model_parameters(model, bootstrap = TRUE, n = 4000)$Coefficient[2]
  )
}
```

## Parent Population
```{r eval=TRUE, message=FALSE, warning=FALSE, results='hide', fig.height=8, fig.width=12}
library(dplyr)
library(ggplot2)

plots(
  generate_parent_population(noise = 0.5, n = 10000) %>%
    ggplot(aes(x = x, y = y)) +
    geom_point(size = 2, alpha = 0.1, shape = 16) +
    geom_smooth(method = "lm", se = FALSE) +
    theme_classic() +
    ggtitle("Noise = 0.5"),
  generate_parent_population(noise = 1.5, n = 10000) %>%
    ggplot(aes(x = x, y = y)) +
    geom_point(size = 2, alpha = 0.1, shape = 16) +
    geom_smooth(method = "lm", se = FALSE) +
    theme_classic() +
    ggtitle("Noise = 1.5"),
  generate_parent_population(noise = 4.5, n = 10000) %>%
    ggplot(aes(x = x, y = y)) +
    geom_point(size = 2, alpha = 0.1, shape = 16) +
    geom_smooth(method = "lm", se = FALSE) +
    theme_classic() +
    ggtitle("Noise = 4.5")
)
```

## Creating Data
```{r eval=FALSE, message=FALSE, warning=FALSE, results='hide'}
parent_model <- lm(y ~ x, data = parent)
parent_coef <- insight::get_parameters(parent_model)[2, 2]

final_data <- data.frame()

for (i in 1:10000) {
  if ((i / 100) %% 1 == 0) print(i)
  cat(".")
  sample <- extract_sample(parent, n = 30)
  model <- lm(y ~ x, data = sample)
  final_data <- rbind(final_data, extract_parameters(model, real = parent_coef))
}
write.csv(final_data, "bootstrapped.csv", row.names = FALSE)
```
